\vskip-0.6in Temporary Trade Barriers: When Will They End?

### 2017-10-03 draft.tex
reverse order of \tau^a and \tau^*a sections; write proof for lemma1

The relationship between $\tau^a$ and break probability is more complex. For any effort level $e$, when the trade agreement tariff is very low, only a small set of realizations of $\ta$ associated with the lowest values of $\ga(e,\ta)$ will lead to approval of the trade agreement, implying a high break probability. As the trade agreement tariff rises, larger values of $\ga(e,\ta)$ are consistent with approving the trade agreement, so the set of $\ta$'s that lead to trade agreement approval is larger. That is, the break probability decreases as $\tau^a$ increases.

\begin{lemma}
  Holding lobbying effort constant, the probability the legislature breaks a trade agreement is weakly decreasing in $\tau^a$.
  \label{res:leg_a}
\end{lemma}

@@

\section{Appendix}
\label{sec:appendix}
\noindent \textbf{\hypertarget{Pr_bincC}{Proof of Result~\ref{res:bincC}}}:\\

>>>>

Let's look first at the direct effect of changing $\tau^a$ on the renewal probability. For any effort level $e$, when the trade agreement tariff is very low, only a small set of realizations of $\ta$ associated with the lowest values of $\ga(e,\ta)$ will lead to approval of the trade agreement, implying a high break probability. As the trade agreement tariff rises, larger values of $\ga(e,\ta)$ are consistent with approving the trade agreement, so the set of $\ta$'s that lead to trade agreement approval is larger. That is, the break probability decreases as $\tau^a$ increases.

\begin{lemma}
  The direct effect of the home trade agreement tariff on the probability the legislature renews the antidumping duty is negative.
  \label{res:leg_a}
\end{lemma}

@@

\section{Appendix}
\label{sec:appendix}
\noindent \textbf{\hypertarget{Pr_leg_a}{Proof of Lemma~\ref{res:leg_a}}}:

Substituting from Equation~\ref{eq:ml}, Equation~\ref{eq:b} can be re-written as
\begin{multline}  
  r(e,\bta,\tad) = \Pr [ \mathit{CS}_X(\tad) + \ga(e,\ve) \cdot \pi_X(\tad) + \mathit{CS}_Y(\tau^{*a}) + \pi_Y(\tau^{*a}) + \mathit{TR}(\tad) >  \\ \mathit{CS}_X(\tau^a) + \ga(e,\ve) \cdot \pi_X(\tau^a) + \mathit{CS}_Y(\tau^{*a}) + \pi_Y(\tau^{*a}) + \mathit{TR}(\tau^a) ]
\end{multline}
Rearranging, we have $r(e_b,\bta,\tad) = $
\begin{multline}  
  \textstyle \Pr \Big[ \frac{\mathit{CS}_X(\tad) + \pi_X(\tad) + \mathit{CS}_Y(\tau^{*a}) + \pi_Y(\tau^{*a}) + \mathit{TR}(\tad)  -\mathit{CS}_X(\tau^a) - \pi_X(\tau^a) - \mathit{CS}_Y(\tau^{*a}) - \pi_Y(\tau^{*a}) - \mathit{TR}(\tau^a)}{\pi_X(\tau^a) - \pi_X(\tad)} + 1 \\ \textstyle < \ga(e,\ve) \Big]
  \label{eq:b_ex}
\end{multline}

The effect on the renewal probability is determined by the sign of the derivative of the left hand side of the inequality in Expression~\ref{eq:b_ex} with respect to $\tau^a$; to show that the break probability is decreasing in $\tau^a$, I must demonstrate that this derivative is positive. Labeling the numerator of that expression $\left[ W(\tad,\tau^{*a})-W(\bta)\right]$ (for the change in social welfare), derivative of this quantity with respect to $\tau^{a}$ is 
\begin{equation}
  \frac{\left(\pi_X(\tad) - \pi_X(\tau^a)\right)\left(\frac{\partial \mathit{CS}_X(\tau^{a})}{\partial \tau^{a}} + \frac{\partial \pi_X(\tau^a)}{\partial \tau^{a}} + \frac{\partial \mathit{TR}(\tau^{a})}{\partial \tau^{a}}\right) - \left[ W(\tad,\tau^{*a})-W(\bta)\right] \frac{\partial \pi_X(\tau^a)}{\partial \tau^a}}{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
  \label{appex:a}
\end{equation}

\noindent $\left(\pi_X(\tad) - \pi_X(\tau^a)\right)$ is always positive. Because the optimal unilateral tariff for large welfare-maximizing governments is positive (call it $\tau^O$), $\left(\frac{\partial \mathit{CS}_X(\tau^{a})}{\partial \tau^{a}} + \frac{\partial \pi_X(\tau^a)}{\partial \tau^{a}} + \frac{\partial \mathit{TR}(\tau^{a})}{\partial \tau^{a}}\right)$ is increasing up to $\tau^O$ and decreasing above it. Thus the first summand is increasing up until $\tau^O$ and decreasing thereafter.

Because total social welfare is maximized at $\tau^a = \tau^{*a} = 0$, $W(\tad,\tau^{*a})-W(\bta)$ is always negative, whereas profits are increasing in $\tau^a$, so the second summand is positive everywhere (inclusive of the leading negative sign). With a positive denominator, we thus have that the derivative is positive on $[0,\tau^O]$.

It is also positive over the remaining $(\tau^O,\tad)$. To see this, add $\left(\tilde{\Gamma} - 1 \right) \frac{\partial \pi_X(\tau^a)}{\partial \tau^a} \left(\pi_X(\tad) - \pi_X(\tau^a)\right)$ to the first summand and subtract it from the second. For any particular value of $\tilde{\tau}^a$, one can choose the $\tilde{\Gamma}$ weight that would make $\tilde{\tau}^a$ the preferred unilateral tariff; this makes the derivative in the first summand zero. Having subtracted the same quantity from the second summand modifies the welfare difference in the second summand to be maximized at $\tilde{\tau}^a$ so that this term is always positive (inclusive of the leading negative sign).

Since the denominator is a squared term of a strictly positive quantity, the expression in Equation~\ref{appex:a} is positive for all $\tau^{a}$.
$\hfill\blacksquare$
